\part{Chapter}
\article{Duties of Officers}

\section The Chairman of the Board of Directors of the Oklahoma Chapter of Triangle shall preside at all meetings of the Chapter, and at all meetings of the Board; he may sign legal documents on behalf of the Corporation; he shall perform such other duties as his office or the Board of Directors may require. In the absence of the Chairman, the Director of Finance shall assume his duties. 

\section The Director of Finance shall have custody of all funds and securities of the Chapter; he shall keep regular books of account; he shall sign instruments requiring his signature; he shall make a complete financial report to the Chapter at the Annual Meeting; he shall be tasked with creation of the budget, and monitoring of its accounting; he shall ensure all steps are require to maintain tax status per the National Organization guidelines; he shall perform all other duties incident to his office, or required by the Board of Directors. The Treasurer shall be bonded. 

\section The Director of Alumni Correspondence shall issue notice of all meetings and keep minutes of the same; he shall keep all Chapter records; he shall maintain a roll of addresses of Chapter alumni; he shall be responsible for the Chapter newsletter and regular announcements to members; he shall sign such legal documents as require his signature; he shall perform other duties incident to his office. 

\section The House Director shall oversee the facilities and chapter equipment; he shall ensure life safety equipment if properly maintained and recommend improvements or updates to facilities as needed; he shall coordinate with and hire contractors on as as-needed basis; and he shall appoint a willing Steward from the chapter for the purpose of overseeing kitchen cleaning, meals, and obtaining other kitchen supplies. 

\section The Director of Alumni Programming shall be responsible for maintaining an events calendar for alumni within and outside the Norman area; he shall promote an environment in which enduring friendships can be maintained for alumni. 

\section The Director of Membership Development shall be responsible for ensuring undergraduate members of the fraternity are on a track for professional success; he shall provide scholastic, resume, professional, or personal help as needed for members; he shall be proactive in his approach in insuring the pipeline of talent is maintained within the chapter. 

\section The Active-at-Large shall provide representation on the Board from the active organization; he shall be charged with representing the needs of the undergraduates and ensuring the Board stays on task and remains central to its core purpose.

\article{Annual Meeting}

\section The order of business at the Annual Meeting of the Board of Directors shall be prepared by the Chairman, making due allowance for presentation of reports, old and new business, submission of amendments to the constitution, and Installation of the officers of the Chapter.

\article{Standing Committees}

\section The Director of Finance will chair the Finance committee. The committee will be responsible for ensuring the strategic financial planning of the chapter. 

\section The Director of Alumni Correspondence will chair the Publicity committee, which will be responsible for ensuring the Alumni are informed on activities pertaining to the actives and alumni of Triangle. 

\section The House Director will chair the House Committee, and is charged with ensuring a healthy and amicable environment is provided for the residents of the fraternity. The House Committee will also recommend improvements to the House Director as needed. The House Manager is a required member of the House Committee. 

\section The Director of Alumni Programming will chair the Programming Committee, which is charged with tasks pursuant to programs relevant to Alumni of the fraternity. 


\part{Active Organization}
\article{Duties of Officers}

\section The President shall preside at all business meetings of the Active Organization; he shall act as the executive officer of the Active Organization; he shall perform such other duties as his officers or the Board of Directors may require; he shall act as the voice of the local organization in all external affairs. The President can form specific committees as circumstances merit. The President can appoint an Independent Greek Council representative to go to their meetings in his place. The President shall have access to, and the responsibility of auditing the chapter finances.

\section The Vice-President shall assume the duties of the President in case of the absence of the President. The Vice-President shall be responsible for Ritual Equipment, and he shall act as supervisor for the pledge program and appoint the Pledge Educator. The Vice-President shall act as mediator in all brotherhood disputes. The Vice-President shall be responsible for the planning and conducting of I-week and Retreat. The Vice-President shall be in charge of a Brotherhood Committee. The Vice-President shall preside at all after meetings of the Active Organization.

\section The Secretary shall keep minutes of all meetings of the Active Organization, and he shall have custody of all records and files of the Active Organization; he shall carry on all regular fraternity correspondence and other correspondence as required by the President. The Secretary is responsible for all mailing and e-mailing lists as well as the maintenance of the chapter’s media; he may appoint someone in his place in the event that he is not able to fulfill these duties. Every two weeks, he is responsible for receiving accountability reports from every applicable officer. At the business meeting before a social event, the Secretary will give details on the accountability reports.

\section The Treasurer shall have custody of all money of the Active Organization; he shall keep accurate electronic records including an archive of all active and alumni balances for at least ten years; he shall collect and disburse funds according to the budget or as directed by the Executive Council; he shall send a monthly statement to alumni with outstanding dues reminding them of their balance. he shall make a complete financial report at one business meeting each month; he shall perform all other duties incident to his office or required by the President; he shall prepare a budget every semester for approval by the Active Organization and National Treasurer. The Treasurer will prepare financial contracts for both semesters and enforce these contracts for both actives and alumni. The accountability report of the Treasurer defines the status of each member with regards to their financial contracts.

\section The House Manager shall have charge of the house and grounds within the constraints of the lease contracts and with approval of the House Director. He shall enforce the house rules, oversee house cleaning, and obtain house supplies. The accountability report of the House Manager consists of attendance of each member during work day or other house cleaning events.

\section The Academics Chair shall promote and encourage the highest possible academic achievement of each active and pledge. The Academics Chair is responsible for scheduling mandatory academics meetings once each academic month with all members and pledges. At the discretion of the Academics Chair, additional mandatory meetings can be held with members whose average overall and previous semester GPA is below 3.0. The accountability report of the Academics Chair consists of records of each member’s attendance at mandatory academics meetings.

\section The Recruitment Chair shall have authority and responsibility in organizing and overseeing all Recruitment related activities. He shall appoint the members of the Recruitment Committee. The accountability report of the Recruitment Chair consists of attendance of each member to every recruitment event.

\section The Social Chair shall have the responsibility of planning major social events, providing brotherhood events, and provide two Greek and two non-Greek social events per year. He is also in charge of communicating and planning with the alumni for Founders’ Day. The accountability report of the Social Chair consists of the attendance of all members at the major social events.

\section The Social Media Chair shall manage all social media accounts held by the active chapter--namely, Instagram and Facebook--and commit to a regular schedule of posts, including but not limited to: flyers for upcoming events; recaps of past events; and recruitment, social, or professional information distributed through our local chapter or through our national or university affiliations.

\section The Philanthropy Chair shall have the responsibility of managing service events, university events, and events within the community. The accountability report of the Philanthropy Chair consists of the records of each member’s fulfillment of the required philanthropy hours.

\section The Risk Management Chair shall have the responsibility of managing risk, ensuring that a safe atmosphere is provided on Oklahoma Chapter of Triangle property and maintaining security during all Oklahoma Chapter of Triangle events. The Risk Management Chair shall appoint a Safety Officer at the start of each academic term.

\section The Safety Officer shall be responsible for ensuring a safe living environment inside Oklahoma Chapter of Triangle property. They shall conduct weekly inspections using a checklist approved by the House Director. They shall be responsible for recommending improvements to Oklahoma Chapter of Triangle property and said property’s life safety equipment.

\article{Standing Committees}

\section There will be four active committees: Recruitment, Brotherhood, Social, and Philanthropy.

\section The Recruitment Committee will formulate an effective rush strategy; plan events and maintain a calendar of events; manage formal rush; and investigate all men proposed for pledging. A majority vote of this committee, with consent of the Executive Council, can bid any person to pledge. It is led by the Recruitment Chair. 

\section The Brotherhood Committee will assist in planning retreat, I-Week, Initiation Ceremony, and other brotherhood events; they will implement and supervise the pledge education program. It is led by the Vice-President.

\section The Social Committee will plan social events, coordinate with other organizations on campus to plan joint events, and coordinate with chapter alumni to plan alumni events. It is led by the Social Chair.

\section The Philanthropy Committee will plan philanthropic events and coordinate with other organizations on campus to plan joint events. It is led by the Philanthropy Chair.

\section Every active member and pledge must be a member of at least one committee; however, a pledge cannot be a part of the brotherhood committee.

\article{Funds}

\section Each member shall pay dues according to their financial contracts as set by the Treasurer and Active Organization. 

\section Any active that receives alumni status while owing the chapter outstanding dues shall repay the active chapter once he is employed. He shall either pay in full or contact the current Active Treasurer to form and agree to a payment plan.

\section During the entirety of a pledge’s pledging semester, each pledge shall pay monetary dues required of him. These monies shall cover the national initiation fee, and the pledge program fees. The Treasurer of the active chapter shall provide to each pledge a detailed bill on how these monies are spent within the first three weeks of pledging. The Treasurer shall also determine the pledge fee during the same meeting as when the semesterly budget is calculated. These monies shall be called due ninety days after the pledge undergoes the pledging ceremony. The balance shall accrue to the general fund of the Active Organization. No part of the initiation fee shall be used for any purpose other than the national initiation pledging fees. 

\article{Pledging}

\section A Pledge can become a member if at the final vote for membership, the final vote consists of less than 20\% negative votes from the actives.

\section Each semester’s pledge class shall elect officers, including, but not limited to, a President, Vice-President, Secretary, and Treasurer. The pledge class President shall report for these officers at each active organization meeting between his election and initiation.

\article{Executive Council}

\section No brother can hold more than one office of the Executive Council.

\section The responsibility of the Executive Council shall be to make decisions on pressing issues.

\section The decisions of executive council can be overturned by a majority vote of the Chapter in any regular business meeting.

\section Executive council must announce all executive council votes as soon as possible.

\article{Judiciary Committee}

\section A Judiciary Committee shall be formed in the event that a dispute occurs that cannot be handled by the Vice-President alone. The Vice-President in this case will nominate three non-partisan brothers to be approved by the Executive Council.

\section If any Executive Council member is involved in the dispute, he must recuse himself of the approval process of the nominees. If the Vice-President is involved, then the duty of nominating the Judiciary Committee will fall on the elected officer who has the lowest bond number and is not involved.

\section Once approved, this committee is to investigate the situation in regards to the Constitution and the Code of Ethics and report to the Active Organization with the course of action.

\section The course of action will be followed unless there is a three-fourth vote at a chapter meeting with quorum present to veto.

\article{Sexual Harassment}

\section Triangle Fraternity has a zero tolerance for sexual harassment as defined by the US Department of State.

\section Upon proof of sexual harassment by a member, a consequence of expulsion will be pursued according to national guidelines.

\article{Drug and Alcohol Policy}

\section The possession, distribution, or use of any illegal or controlled substances without a legal prescription on the chapter property, at a sponsored event, or in any other situation that could associate a member with the possession, distribution, or use of any illegal or controlled substances is strictly prohibited.

\section The possesion of hard alcohol, defined as any beverage with an alcohol content of greater than or equal to 15 percent alcohol by volume, shall be prohibited in all rooms of the Chapter House, including in private rooms, except when provided under the control of a licensed, insured third-party vendor.

\section Any incident violating this premise will require the President to propose the expulsion of the violating party.

\article{Financial Accountability}

\section By the second business meeting of each semester, every active member will setup a payment contract for the upcoming semester dues, to be paid in full.
\begin{itemize}
    \item Partial payment plans are to be determined by the active Treasurer on a case-by-case basis. All partial payment plans will need to be approved by executive council.
    \item Each payment contract will cover no less than National fees, insurance fees, and any additional chapter operational fees deemed necessary by the active Treasurer.
    \item As long as payment is still owed, payments may be made no less frequently than the seventh of each month starting with the first full month of the semester.
\end{itemize}

\section Delinquent payments are to be defined as any amount of unpaid monies as agreed upon in the payment contract by the agreed payment date. Any delinquent payments will be paid as soon as possible.
\begin{itemize}
    \item A delinquent payment must be resolved with the Treasurer to be paid in full or by amending the current payment contract to make up the delinquent payment. Either option must be resolved by the next payment date according to your current payment contract.
    \item A payment strike is to be defined as any breach in your payment contract, including missing a payment or failing to resolve a delinquent payment by the next payment cycle. Any strikes will remain on your record for the duration of the academic year the strike was given.
    \item The first strike will result in a warning by the Treasurer.
    \item The second strike will result in the active member being barred from any function of the chapter that does not fall under the membership accountability index. This punishment is absolved once all delinquent payments are resolved. 
    \item The third strike will result for an immediate call to vote, by the Treasurer, for expulsion of the offending member from the Oklahoma Chapter of Triangle. If the vote does not pass, an immediate call to vote by the Treasurer for suspension of the offending member from the Oklahoma Chapter of Triangle. If the vote for suspension does not pass, an emergency meeting will be called by the Chapter President immediately following the chapter meeting to resolve the issue.
    \item All members reserve the right to appeal to reverse a strike. All appeals are to be made during the next business meeting, and are passed by two-thirds of present members.
\end{itemize}

\section In the event that an active member wants to change his payment contract, he must set up a meeting with the active Treasurer to discuss any changes in payment cycles or payment amounts. Any proposed changes must follow the same guidelines for setting up a preliminary contract. Any changes must be approved by the active Treasurer and no less than two other executive council members. Payment contracts can only be changed up to twice a semester, and no more than once per month.

\article{Live-In Policy}

\section Every active member is required to live in the chapter house for a minimum of two semesters as soon as they are eligible, unless decided otherwise by a three-fourths (3/4) vote by the active chapter.

\section Any individual breaking the lease at any point during the required semesters will require the house manager to propose a vote to the active chapter for the individual to be suspended.

\section Failure to sign a lease for the required semesters as soon as the member is eligible to live in house will require the house manager to propose a vote to the active chapter for the individual to be expelled.

\article{Accountability}

\section If a member of the Active Organization misses a chapter meeting for an unexcused reason, the member will lose their right of vote. In the event of a second unexcused absence, the member will also lose their right of voice and their right to attend to social events. A member can restore the rights that they have lost by attending all chapter meetings for two consecutive weeks.

\section If a member of the Active Organization misses more than one work day in a month for an unexcused reason, the member will lose the right to attend social events and chapter dinner, until said brother is caught up on work days. Work days can be made up by the House Manager’s approval.

\section If a member of the Active Organization fails to attend a required academics meeting as defined by the Academics chair, they will lose their right to attend social events. The member may have this right restored by making up the missed meeting in a manner deemed acceptable by the Academics Chair.

\section If a member of the Active Organization misses more than one-fifth of the recruitment events during a semester for unexcused reasons, they lose the right to have a little brother for that semester.  

\section If a member of the Active Organization fails to meet their required philanthropy hours by the cuttoff(s) determined by the Philanthropy Chair, they will lose their right to attend social events. The member may have this right restored by making up the hours in a manner deemed acceptable by the Philanthropy Chair.

\article{Parliamentary Authority}

\section The rules contained in the tenth edition of Robert's Rules of Order Newly Revised shall govern the Active Organization in all cases to which they are applicable and in which they are not inconsistent with these bylaws, any special rules of order the Active Chapter may adopt, and any statutes applicable to the Active Organization that do not authorize the provisions of these bylaws to take precedence.

\article{Special Rules of Order}

\section If both the President and Vice-President know they shall be absent from a meeting, the President shall appoint a President pro tem. to preside over the meeting in his place. The President pro tempore's office will terminate in the event of the arrival of either the President or Vice-President, or by a majority vote to elect a new President pro tem.

\section If the Vice-President knows he shall be absent from a meeting, he shall apoint an officer to preside over aftermeetings in his place. This office will terminate in the event of arrival of the Vice-President, or by a majority vote to elect a new presiding officer.
