\part{Chapter}
\article{Name and Object}

\section This organization shall be known and designated as "Oklahoma Chapter of Triangle," by virtue of the charter granted to it on November 18, 1979, by TRIANGLE, a Fraternity of Engineers, Architects, and Scientists.

\section The objective of the Oklahoma Chapter of Triangle shall be the objective of TRIANGLE, as stated in the National Constitution of Triangle. It shall carry out its object by maintaining a chapter of TRIANGLE and a fraternity home for its members at the University of Oklahoma.

\section Any section or bylaw of this constitution not in accord with the National Constitution or the Ritual of TRIANGLE shall be void, and shall be amended, as hereinafter provided.

\article{Membership and Organization}

\section The members of the Oklahoma Chapter of Triangle shall be all men who have been regularly initiated into the chapter, and all Honorary, Associate, and Affiliated members of the chapter, as defined in Article 3 of the National Constitution and Article 1 of the National Bylaws. It shall also include naturalized members of other chapters as defined in Section 6 of this Article. This Constitution defines a “Brother” to be a person who meets the requirements of membership at any chapter of TRIANGLE.

\section The Chapter shall consist of an Alumni Organization and an Active Organization, as hereinafter described.

\section The government of the Oklahoma Chapter of Triangle shall be vested in a board of directors, as hereinafter provided.

\section The Oklahoma Chapter of Triangle shall be incorporated under the laws of the State of Oklahoma. If the corporate name of the chapter differs from its fraternal name, the corporate name shall be used in legal matters only.

\section The Corporation shall be governed according to this constitution, and according to its legal contracts.

\section Under the authority granted in the National Constitution, Article 1, Section 2, Paragraph 4, the Oklahoma Chapter of Triangle may designate certain brothers of other chapters as naturalized members of Oklahoma Chapter. Such brothers should be brothers who have shown an ongoing desire to be a part of Oklahoma Chapter, its activities and culture. To be recommended as a naturalized member, the brother must have attended at least one Initiation Ceremony with our chapter and be an alumnus of his own chapter.

\section Any current member of Oklahoma Chapter (including already naturalized members) may recommend a brother for this special status by making a motion to the Board of Directors, either in one of its regular meetings or by e-mail to the entire Board. The Board will announce the nomination to all current Oklahoma members prior to the Annual Meeting in whatever communications medium the Board sees as best for the time period. The vote will be taken at the Annual Meeting by secret ballot of those Oklahoma members present. The nominee must receive no more than 3 no votes to be granted naturalized status. A naturalized brother may take part in Oklahoma Chapter affairs to the same extent as any regular alumnus member while retaining membership in his original chapter. The next available page in the Oklahoma Chapter member book shall be used to record the naturalized member, though his place in chapter activities involving bond number shall be by his national bond number.

\article{Meetings}

\section An annual meeting of the Board of Directors shall be held on the same day as the Local Founders’ celebration at the Chapter House. This, and all other meetings, shall be open to all members of the Fraternity.

\section Special meetings of the Board of Directors may be called at any time, when authorized by a majority vote of the Board of Directors, or upon written or email request of ten (10) members of the Chapter to the Board of Directors.

\section At least fourteen (14) days notice, in writing or email, shall be sent to all Members for both annual and special meetings.

\section A quorum at any meeting of the Board of Directors shall consist of a majority of voting members. Persons designated as proxy voters shall count toward quorum requirements.

\section The Board of Directors will set a uniform policy by which Members of Triangle who are not members or voting proxies of members of the Board of Directors will be afforded the opportunity to raise issues and opinions at meetings of the Board of Directors.

\article{Board of Directors}

\section The Board of Directors shall consist of:
\begin{itemize}
\item The Chairman
\item The Director of Finance
\item The Director of Alumni Correspondence
\item The House Director
\item The Director of Alumni Programming
\item The Director of Membership Development
\item The Active-at-Large
\end{itemize}

\section It shall be the duty of the Board to responsibly grow the Alumni and Active Organization, in whole and in part, and execute the business of the fraternity; it shall be ultimately responsible for the health of the organization and brotherhood. It shall make a complete report of the status of the Chapter at each Annual Meeting. 

\section The Board of Directors shall administer the funds of the Chapter, and it shall authorize the disbursement of funds for such general purposes as the Chapter may direct. It shall serve as the governing body of the Oklahoma Chapter Corporation.

\section The members of the Board of Directors are chapter-wide offices and shall be elected by popular vote of the Active, Alumni, Associate, and Honorary membership of the Chapter.

\section The members of the Board of Directors must be elected by secret ballot. 

\section The members of the Board of Directors shall be installed at the Annual Meeting of the Board of Directors during even-numbered years. They shall serve 2 year terms. There are no term limits on the positions for the Board of Directors.

\section One person may not be elected to more than one office on the Board of Directors at a time. At no time shall any member of the Board of Directors cast more than one vote on any matter

\section The Chairman, Active-At-Large, and Directors of Finance, Alumni Correspondence, Alumni Programming, and Membership Development must all be members of Triangle Fraternity, though they need not initiated into the Oklahoma Chapter. All other positions may be held by non-Triangle members.

\section A new board position can be added at the unanimous consent of the Board of Directors. These members are considered full voting members of the Board of Directors and serve in the designated capacity and defined title. These ad-hoc positions may be removed by unanimous consent of the core officer listed in Section 1.

\section Members can be removed by 3/4 vote of no-confidence. Vacancies are appointed by the Chair to serve the remaining term. If the Chair is removed, a new chair is elected by the remaining board members.

\article{Duties}

\section The Board of Directors shall elect and send an alumnus delegate to each National Convention of TRIANGLE.

\section The Board of Directors shall finance the preparation and mailing of all chapter newsletters.

\section Amendments shall be sent to the National Headquarters for the purpose of keeping the copy of the chapter constitution there up to date.

\article{Amendments and Bylaws}

\section The Annual Meeting of the Board of Directors shall consider any amendment to this constitution which is submitted to it in writing with recommendation for approval by either by the Active Organization or by the Board of Directors.

\section Any amendment so submitted shall be adopted if it receives the favorable vote of three-fourths (3/4) of the members at the Annual Meeting of the Board of Directors. 

\section The Bylaws to this constitution may be amended by a two-thirds (2/3) favorable vote of the members present at the Annual Meeting of the Board of Directors, or by the unanimous vote of the Board of Directors.

\article{Limitations and Obligations of Officers}

\section The officers of this organization serve at the request of, and as a result of election by, the membership of the organization, and assume no personal responsibility for the debts and obligations of the Oklahoma Chapter of Triangle as a result of their service or the execution by them of documents on behalf of the Oklahoma Chapter of Triangle. The Oklahoma Chapter, its creditors, and its assignees shall have no claim against the personal assets of the officers, individually or severally, except to the extent that a court of competent jurisdiction shall determine that such officers have incurred a liability by reason of fraud, deliberate and willful misconduct, or mismanagement so gross as to constitute fraud.

\article{Transfer of Assets/Liabilities on Dissolution}

\section In the event that the Active/Student organization of the Oklahoma Chapter of Triangle Fraternity shall cease activities, dissolve, or disband, whether voluntarily or involuntarily, all assets of the Oklahoma Chapter of Triangle shall remain in the possession of the University of Oklahoma Chapter of Triangle Fraternity, Inc.

\section In the event that this Chapter along with its Corporation entity shall cease activities, dissolve, or disband, whether voluntarily or involuntarily, the assets of the Oklahoma Chapter of Triangle shall be transferred to the National Council of Triangle which shall apply such assets to the satisfaction of outstanding liabilities and thereafter shall hold or dispose of the unexpended balance of assets, if any, in a manner satisfactory to the National Council of Triangle.


\part{Active Organization}
\article{Membership}

\section The Active Organization of the Oklahoma Chapter of Triangle (referred to hereafter as Active Organization) shall consist of all members initiated into Triangle Fraternity who are enrolled at the University of Oklahoma, have not attained alumni status, and have not been expelled from any chapter of Triangle.

\section Active members shall be chosen from students enrolled at the University of Oklahoma whose course of study leads to a degree that has been approved by the active chapter.

\section Alumni status from the Oklahoma chapter of Triangle may be awarded after 8 active semesters (including pledgeship), completion of a Bachelor's Degree or higher from the University of Oklahoma while active with the Oklahoma Chapter of Triangle after one semester of active status with the Oklahoma Chapter of Triangle, or by two-thirds favorable vote of the Active Organization and majority vote of the Board of Directors.

\section Those who are no longer enrolled in the University of Oklahoma during a fall or spring semester and have not received local alumni status are not allowed on Oklahoma Chapter of Triangle property unless otherwise overruled by a two-thirds (2/3) favorable vote of the Active Organization. A vote to reconsider this overrulling may be motioned in future semesters. In the event that they return to the University of Oklahoma, but not to the Oklahoma Chapter of Triangle, they will be put to a vote of expulsion as seen by the vice president of the Active Organization.

\article{Elected Officers}

\section The elected officers of the Active Organization shall be the President, Vice-President, Secretary, Treasurer, House Manager, Academics Chair, Recruitment Chair, Social Chair, Social Media Chair, Philanthropy Chair, and Risk-Management Chair.

\section This section defines procedure for a regular election. At least two men members or pledges of the Oklahoma Chapter of Triangle shall be nominated for each office. Nominations for all offices except House Manager and Risk Management shall take place during the last business meeting of the month of October. Nominations for House Manager and Risk Management shall take place during the last business meeting of the month of March. The elections shall take place at the next regular business meeting. The candidate receiving a plurality vote of the members present shall be declared elected to office for one year. In case no candidate receives a plurality vote, a new ballot shall be taken, with the two men receiving most votes on the previous ballot being the new nominees.

\section This section defines procedure for a special election. A special election shall be held any time a position needs to be filled outside of the normal election period. At least one man shall be nominated for each vacant office at either the business meeting of the vacancy or the next possible business meeting. The candidate receiving a plurality vote of the members present shall be declared elected to office until the next regular election period. In case no candidate receives a plurality vote, a new ballot shall be taken, with the men receiving the most votes on the previous ballot being the new nominees.

\section Nominees shall have a cumulative grade point average of 2.75 from the University of Oklahoma. Officers whose cumulative grade point average falls below this criteria shall resign and be replaced through special election.

\section Newly elected officers shall be installed at the first business meeting of the academic semester after their election.

\section Any officer may be removed from office by a two-thirds vote of the Active Organization, provided that notice was given at the previous business meeting.

\section Executive council shall consist of the Active President, Vice-President, Secretary, Treasurer, and Risk-Management.

\section If an officer, either elected or appointed, is slain by another brother in single combat, the fratricide shall take over that officer position. In the event that the officer is slain by a conspiracy of two or more brothers, the fratricide with the highest bond number will take over the post of the slain.

\article{Meetings}

\section A business meeting shall be held each week of the school year, except the week of spring break, the fall Thanksgiving break, and the week of Final Examinations. Alumni can vote in the active chapter meetings if they hold an office in the active organization. Members of the chapter who currently maintain active status with Triangle nationally, but are not enrolled (including but not limited to those on co-ops, internships, and study abroad) can vote in the active chapter meetings if they are in attendance.

\section Upon majority vote of executive council, special meetings may be called at any time. If less than one weeks notice is given for a special meeting, then no punishment may be assessed for lack of attendance.

\section A quorum shall consist of three-fourths of the members of the Active Organization who have recieved voting rights.

\article{Amendments and Bylaws}

\section An amendment to Part II of this constitution must be submitted in writing at a business meeting of the Active Organization, but cannot be voted upon until the following business meeting.

\section A submitted amendment shall be adopted if it receives a two-thirds favorable vote when a quorum is present.

\section The Bylaws to Part II of this constitution may be altered by a favorable vote when quorum is present at business meeting.

\section Following favorable vote the alteration to the constitution will be submitted for approval in writing to the Annual Meeting of the Board of Directors.
