\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\hypersetup{}
\usepackage{calc, tocloft, etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
\apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother


\title{\textsc{Oklahoma Chapter of Triangle}}
\subtitle{\textsc{Membership Accountability Criteria}}

\begin{document}

\maketitle

% Adjust paragraph spacing
\setlength\parindent{0pt}

As a member of Triangle Fraternity, I recognize my obligation to do the following each semester:

\begin{enumerate}
    \item Observe the precepts of the fraternity as set forth in the Ritual
    \begin{enumerate}
        \item Attend all Ritual Ceremonies unless there is an emergency, illness, or a conflict prior discussed with the Vice President no less than 2 months in advance.
        \item Protect the secrets of the fraternity from all non-members.
        \item Desire to live in conformance with the stated values of the Ritual.
        \item Get voting rights during first semester as an active member.
    \end{enumerate}
    \item Accept cheerfully my full share of any task, however menial, involved in maintaining my chapter home
    \begin{enumerate}
        \item Attend all workdays unless otherwise excused. Missed workdays may be made up by performing work to the satisfaction of the house manager.
        \item Take responsibility for all damage caused by yourself or your guest.
    \end{enumerate}
    \item Preserve and promote the chosen ideals of my Fraternity
    \begin{enumerate}
        \item Participate actively in the initial stages of recruitment which includes generating lists of potential new members, calling potential new members, and meeting potential new members.
        \item Participate actively in the closing stages of recruitment which include introducing potential new members to Triangle and pre-closing potential new members.
        \item Attend 50\% of all business meetings.
    \end{enumerate}
    \item Pay all personal bills promptly, and always live within my means
    \begin{enumerate}
        \item Pay all Fraternity dues agreed upon in your financial contract, signed at the beginning of each semester.
    \end{enumerate}
    \item Help create in my chapter home an environment in which enduring friendships may be formed
    \begin{enumerate}
        \item Respect the beliefs and feelings of other Brothers.
        \item Resolve all conflicts with other brothers promptly, personally, and in a respectable manner.
    \end{enumerate}
    \item Maintain a creditable scholastic record
    \begin{enumerate}
        \item Maintain a cumulative GPA that is above 2.5. A brother below a 3.00 will be placed on academic probation with further actions required by the Academics chair (e.g. study hours, tutoring, etc), and a restriction on social events unless their current academic progress is deemed acceptable by the Academics chair.
        \item Those that are undergoing the new member process must have a minimum of a 3.00 GPA on a 4.00 scale in order to initiate, without exception.
    \end{enumerate}
    \item Promote the welfare of my profession
    \item Maintain my self-respect by proper conduct at all times
    \begin{enumerate}
        \item Avoid any charge by the Police, any charge of academic dishonesty by Oklahoma University, any incident of drunk driving, any physical or sexual assault of another, any theft of or damage to another’s property, or engaging in the use or possession of illegal drugs within the Fraternity House or during a Fraternity event.
        \item Strive to avoid any action which would result in the active chapter taking action; take responsibility for any actions resulting in active chapter action, and adhere faithfully to the decision of the chapter.
    \end{enumerate}
    \item Uphold faithfully the traditions and program of my Alma Matter
    \item Pay the price of success in honest effort
    \begin{enumerate}
    \end{enumerate}
\end{enumerate}

Key Metrics

\begin{enumerate}
    \item Attend 50\% of Business Meetings calculated at the 4th business meeting.
    \item Attend all Ritual ceremonies unless there is an emergency, illness, or conflict prior discussed with the Vice President no less than 2 months in advance.
    \item Participate in 5 events of any type (Philanthropy, Recruitment, Social, etc) per semester, in some capacity.
    \item Pay dues and rent by the end of the respective semester, unless otherwise arranged with the Treasurer.
    \item Maintain a cumulative GPA that is above a 2.50. New members must have a cumulative GPA of at least 3.00 in order to initiate.
    \item Avoid any charge by the Police, any charge of academic dishonesty by Oklahoma University, any incident of drunk driving, any physical or sexual assault of another, any theft of or damage to another’s property, or engaging in the use or possession of illegal drugs within the Fraternity House.
\end{enumerate}

Any Brother not upholding all key metrics shall have their “Active Brother Status” reviewed\footnotemark by the active chapter.

\footnotetext{Reviewed meaning discussion of said brother’s future with the chapter at business meeting. Upon status review of a member in question, the chapter has the option to send the infraction to the Standards Board for review.}

\end{document}
