\begin{enumerate}
\item The Chapter will pay for intramural fees of members and their friends representing Triangle, subject to chapter approval. 
\item There will be a twenty-five dollar charge for bounced checks to the Chapter. 
\item There will be no smoking or vaping in public areas of the house.  
\item Pledges are not to be charged for parties and banquets.  
\item Members must cover the cost of their parents at banquets.  
\item National active dues at initiation will be paid by the Alumni chapter if the new initiate had a 4.0 GPA the final semester of pledgeship if they were a full time student.
\item The chapter newsletter shall be named The Event Horizon. 
\item If a member questions another members personal hygiene, then the member in question will have 24 hours to fix the problem.
\item There shall be an alumni mailing list on the outriangle.org domain. This list shall maintain archives which Active Members may examine.
\item A mug may only be used by its creator or if it was made by an alumnus long past.
\item Everyone must flush the toilet after use.
\item There will be no illegal torrenting at the manor.
\item Only Pledges, Actives, Manor Superintendent, Alumni, House Director, Associate Members, Honorary Members, Distinguished Fellows of Triangle, or those designated by the Manor Superintendent can know the manor door code.
\item There will be no coitus in the community showers of the house.
\item The organization shall be referred to as a fraternity, and not a frat.
\item City-provided waste bins will be placed within 2 feet of the curb after 12:00 PM on the day before pickup and returned to their storage location no later than 12:00 PM the following day, as per City Ordinances Section 21-201(e). City administrative fees for non-compliance will be assessed against the member who volunteered to perform the task, or evenly distributed among all members if there was not a volunteer.
\item Trash cans will be emptied when full.
\item The Chapter acknowledges that it is illegal to dispose of grease trap waste, waste fats, waste oils, and/or waste grease in the city-provided waste bins. Members will arrange to properly dispose of this waste.
\item Dishes shall be rinsed and racked properly per the Hobart AM-14 operations guide.
\item Members shall clean all spills made during cooking.
\item The ovens shall not be left on when not in use.
\end{enumerate}
